### 2014-07-30 Studies/2012_Chicago/Report/Chicago_Fire.tex
Chicago: Minor edit

As discussed in Section~\ref{geom}, the structure has dimensions of 17.15~m (56~ft) by 6.15~m (20~ft) and a total height of 8.56~m (28~ft). To ensure adequately resolved fluid flow in and out of the structure, the computational domain was extended beyond the volume of the structure. The total volume of the computational domain was 24~m (79~ft) by 10~m (33~ft) by 10~m (33~ft). At a grid resolution of 10~cm (3.9~in), this would result in 2.4 million computational cells. To make the simulation time more reasonable (a run time of approximately one and a half days), the domain was divided into 16 equal meshes (each containing 150 thousand grid cells) to be processed in parallel. Figure~(\ref{fig:mult_mesh}) shows the entire structure within the computational domain that has been divided into multiple meshes. For the simulations that were conducted as part of this study, Table~\ref{tab:mod_param} shows the relevant model input parameters that were discussed in Section~\ref{model}.

>>>>

As discussed in Section~\ref{geom}, the structure has dimensions of 17.15~m (56~ft) by 6.15~m (20~ft) and a total height of 8.56~m (28~ft). To ensure adequately resolved fluid flow in and out of the structure, the computational domain was extended beyond the volume of the structure. The total volume of the computational domain was 24~m (79~ft) by 10~m (33~ft) by 10~m (33~ft). At a grid resolution of 10~cm (3.9~in), this results in 2.4 million computational cells. The domain was divided into 16 equally sized meshes (each containing 150,000 grid cells) that could be processed in parallel, which reduced the amount of required calculation time to approximately 1.5~days. Figure~(\ref{fig:mult_mesh}) shows the entire structure within the computational domain that has been divided into multiple meshes. For the simulations that were conducted as part of this study, Table~\ref{tab:mod_param} shows the relevant model input parameters that were discussed in Section~\ref{model}.
